### 2022-06-07 main/chapter_2ljets.tex
add first draft high region def text

\subsection{Splash summary}
\label{sec:2ljets_splash}
% begin with physics content and results

Unblinded results in all main regions of the $\twoljets$-electroweak analysis
are presented in of the Figure~\ref{fig:2ljets_summary}.
Since this figure appears to represent the data and background estimates,
on which all derived results depend, it could be seen as the keystone of this
thesis.
There are, however, caveats to be developed later in this chapter.

@@

@@

\FloatBarrier
\section{Design}
The most impactful decision in a search is the design of its regions.
Like all decision in life, these designs must be made to balance conflicting
and vaguely-specified desires, and are informed with incomplete information.

@@

The clearest idea behind this design is to split regions on $\metsig$.
Motivation for this design is displayed in
Figure~\ref{fig:2ljets_presel_met};
$\metsig$ does better than $\met$ in separating background and signal
contributions for models with various mass splittings above $m(Z)$.
But there is more --- $\metsig$ also decently separates signal models from one
another;
signals with larger mass differences in their decays to invisibles tend to have
larger $\metsig$.
Binning regions in $\metsig$ therefore also improves sensitivity to
individual parameter points and allows targeted selections on other,
locally-relevant, event variables.

@@

Control and validation regions are defined to constrain the background
modelling in all regions.

Table~\ref{tab:2ljets_presel}
\TODO{define presel, preselection SFOS 25 1J met>100 metsig>6}

@@

Figure~\ref{fig:2ljets_region_summary}

\begin{table}[tp]
\centering
\begin{tabular}{c}
Pre-selection:
\\[1em]
$n_\mathrm{leptons}^\mathrm{signal} = n_\mathrm{leptons}^\mathrm{baseline} = 2$
\\[0.5em]
same flavour, opposite charge leptons
\\[0.5em]
$\njet \geq 1$
\\[0.5em]
$p_\mathrm{T}^{\,\ell_2} > 25$
\\[0.5em]
$\met > 100$
\\[0.5em]
$\metsig > 6$
\end{tabular}
\caption{%
`Pre-selection' requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search.
}
\label{tab:2ljets_presel}
\end{table}

\subsection{High}
\label{sec:2ljets_high}
Table~\ref{tab:2ljets_high}
Figure~\ref{fig:2ljets_high_mll_b}
Figure~\ref{fig:2ljets_high_region}
Figure~\ref{fig:2ljets_high_1J_region}
Figure~\ref{fig:2ljets_high_llbb_region}

@@

\section{Validation}

Figure~\ref{fig:2ljets_low_crz_extensions}
Figure~\ref{fig:2ljets_splits}

>>>>

\subsection{Splash summary}
\label{sec:2ljets_splash}
% begin with physics content and results
Unblinded results in all main regions of the $\twoljets$-electroweak analysis
are presented in of the Figure~\ref{fig:2ljets_summary}.
Since this figure appears to represent the data and background estimates,
on which all derived results depend, it could be seen as the keystone of this
thesis.
There are, however, caveats to be developed later in this chapter.

@@

\subsection{Jet pairs}
\TODO{why leading two jets mjj / rjj}

@@

\FloatBarrier
\section{Design}
Perhaps the most impactful decision in a search is the design of its regions.
Like most decision, these designs must be made to balance conflicting and
vaguely-specified desires, and are informed with incomplete information.

@@

The clearest idea behind this design is to split regions on $\metsig$.
Motivation for this design is displayed in
Figure~\ref{fig:2ljets_presel_met};
$\metsig$ does better than $\met$ in separating background and signal
contributions for models with various mass splittings above $m(Z)$.
Furthermore, $\metsig$ also works to separate signal models from each other;
signals with larger mass differences in their decays to invisibles tend to have
larger $\metsig$.
Binning regions in $\metsig$ therefore also improves sensitivity to
individual parameter points and allows targeted selections on other,
locally-relevant, event variables.

@@

Following the conventional style descibed in
Section~\ref{sec:sec:searches_searches},
control regions are defined to normalize specific background samples,
and validation regions are defined to test their extrapolation towards
signal regions before unblinding.

All regions are defined within a loose `Pre-selection' requirement which
requires the basic $Z\rightarrow \ell^+\ell^-$ plus jets pluts $\met$
conditions that we target in the $\twoljets$-electroweak.
These Pre-selection requirements are defined in Table~\ref{tab:2ljets_presel}.

@@

A high-level summary of the region design is shown
Figure~\ref{fig:2ljets_region_summary}.
The design comprises four control regions and thirteen orthogonal signal region
bins, with validation regions targeting each group of signal regions.

\begin{table}[tp]
\centering
\begin{tabular}{c}
Pre-selction
\\[1em]
$n_\mathrm{leptons}^\mathrm{signal} = n_\mathrm{leptons}^\mathrm{baseline} = 2$
\\[0.5em]
same flavour, opposite charge leptons
\\[0.5em]
$\njet \geq 1$
\\[0.5em]
$p_\mathrm{T}^{\,\ell_2} > 25$
\\[0.5em]
$\metsig > 6$
\\[0.5em]
$\met > 100$
\end{tabular}
\caption[%
Pre-selection requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search
]{%
Pre-selection requirements ensured prior to all region definitions in the
$\twoljets$-electroweak search.
Although $\metsig > 6$ implies that most events already have large $\met$
$\met > 100\,\eV[G]$ requirement is included to ensure that events with small
$\met$ and smaller uncertainties on it are excluded.
}
\label{tab:2ljets_presel}
\end{table}

\subsection{High}
\label{sec:2ljets_high}
The highest $\metsig$ selections, of around $\metsig > 18$, contain almost pure
diboson backgrounds in relatively small quantities, along with the bulk masses
of signal samples at the heaviest resonance masses.
This is therefore the most promising territory for signal regions which are
highly sensitive to the most extreme signals.
Their backgrounds, however, must be constrained by control regions in less
extreme parameter spaces with more data.

Diboson backgrounds and C1N2 signals have more in common than just $\met$.
Notably, both also produce resonant $Z\rightarrow \ell^+\ell^-$ pairs
and do not enhance the rate of heavy-flavour jets, as displayed in
Figure~\ref{fig:2ljets_high_mll_b}.
Since signals and backgrounds have such similar shapes in $\mll$ and $\nbtag$,
sensitivity is only decreased by rejecting portions of these distributions.
Although most $\twoljets$-electroweak regions use tighter selection on these
variables to reduce backgrounds, this observation allows us to win
additional sensitivity in High regions by loose requirements.

The $\mll \in 71\textrm{--}111$ window loosely selects the $m(Z)$ peak to
scoop up nearby rare of mismeasured events.
Similarly, allowing up to one $b$-tag improves yields without boosting
backgrounds since the $\metsig$ requirement already removes most $\ttbar$
processes.

The standard wide $\mjj \in 60\textrm{--}110\,\eV[G]$ requirement captures
both $W\rightarrow jj$ and $Z\rightarrow jj$ for C1N2 and GMSB models
respectively.

The high regions, defined in Table~\ref{tab:2ljets_high}, comprise SR-High,
SR-High-1J, and SR-$\llbb$.
To maximize projected sensitivity, SR-High is split into four bins with
splits at $\rjj = 0.8$, to form SR-High-8 and SR-High-16, and second at
$\metsig = 21$ to split these into SR-High-*-a and SR-High-*-b.
For example, SR-High-8-b requires $\rjj < 0.8$ and $\metsig > 21$.
The regions SR-High-8 and SR-High-16 are displayed in
Figure~\ref{fig:2ljets_high_region}, with their -a and -b bins visible across
the $\metsig$ distribution.

One major difference between signals and diboson backgrounds is that signal
jet pairs mostly arise from boosted $W\rightarrow jj$ decays which more often
produce nearby jets.
Selecting small $\rjj$ in SR-High therefore picks out these boosted cases.

Extremely boosted $W$ bosons can be clustered into single jets.
Although large-radius jets are typically used to capture these, we only use
small, $R=0.4$, jets in the $\twoljets$ analysis.
And those small jets can work for the extreme boosts that our signals produce.
To catch these extreme events is the goal of SR-High-1J, which is displayed
in Figure~\ref{fig:2ljets_high_1J_region}.

All other regions require two jets or more, so this single-jet selection has
the liberty to reduce its $\metsig$ requirement to $\metsig > 12$
without overlapping any other regions.

Finally, SR-$\llbb$ is designed to target the GMSB model, which produces decays
via $ZZ$ and $Zh$ bosons pairs.
Since the $h\rightarrow bb$ branching fraction is large, SR-$\llbb$ finds
sensitivity by requiring a pair of $b$-tagged jets in a heavy mass window.
The low edge of this $\mbb \in 60\textrm{--}150\,\eV[G]$ window is chosen not
only to accommodate \atlas' noisy reconstruction of $b$-jets, but also to
capture $Z\rightarrow bb$ decays, which become significant signal models with
small $B(\neutralino_1 \rightarrow h \gravitino)$.

As shown in Figure~\ref{fig:2ljets_high_llbb_region}, backgrounds in SR-$\llbb$
contain a significant proportion of rare top quark processes;
studies presented in Section~\ref{sec:2ljets_validation} show that these are
mainly $t\bar t Z$.

@@

\section{Validation}
\label{sec:2ljets_validation}
Figure~\ref{fig:2ljets_low_crz_extensions}
Figure~\ref{fig:2ljets_splits}
